Expression QTL hotspot dissection with mediation analysis and pleiotropy testing

### 2019-06-19 analysis/paper/paper.Rnw
documentclass{book} -> {article}
removed unneeded packages

\documentclass[oneside]{book}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[utf8]{inputenc}
\usepackage{lineno}
\linenumbers

@@

\usepackage[
    backend=biber,
    style=chicago-authordate,
%    citestyle=authoryear,
    natbib=true, %citet and citep
    url=true,
    doi=true,
    eprint=true,
    maxbibnames=10,
    backref=true
]{biblatex}
\DeclareLanguageMapping{english}{english-apa}
\addbibresource{research.bib}
\usepackage{graphicx}
\usepackage{color, colortbl}
\definecolor{LightCyan}{rgb}{0.88,1,1}
\usepackage{subcaption}
\usepackage{array}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{longtable}
\usepackage[outdir=./figs/]{epstopdf}
\usepackage{etoolbox} % for messing with page style & title pages
\usepackage{fancyhdr}
\setlength{\headheight}{15.2pt}
\pagestyle{fancyplain}
\fancyhf{}
\lhead{}
\chead{}
\rhead{ \fancyplain{}{\thepage} } % put page number in upper right corner
\rfoot{Compiled on \today\ at \currenttime}
\renewcommand{\headrulewidth}{0pt} % remove top line
\renewcommand{\footrulewidth}{0pt} % remove bottom line
\renewcommand{\headrule}{}

\title{Expression QTL hotspot dissection}
\author{Frederick J. Boehm, Brian S. Yandell, and Karl W. Broman}
\date{\today}

@@

<<include=FALSE>>=
library(knitr)
opts_chunk$set(
concordance=TRUE,
echo = TRUE,
fig.lp = "fig:",
warning = FALSE,
message = FALSE)
@

\doublespacing
\tableofcontents
\listoffigures
\listoftables
%\pagestyle{headings} % page numbers appear at bottom of page, centered!
%\markright{\hfill}
\chapter{Introduction}

@@

@@

<<r install_here>>=
install.packages("here", repos = "https://cloud.r-project.org")
@

@@

<<r colophon, cache = FALSE>>=
# which R packages and versions?
devtools::session_info()
@

@@

<<r git2r, cache = FALSE>>=
# what commit is this file at?
git2r::repository(here::here())
@

>>>>

\documentclass[]{article}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[utf8]{inputenc}
\usepackage{lineno}
\linenumbers

@@

\usepackage[
    backend=biber,
    style=chicago-authordate,
%    citestyle=authoryear,
    natbib=true, %citet and citep
    url=true,
    doi=true,
    eprint=true,
    maxbibnames=10,
    backref=true
]{biblatex}
\DeclareLanguageMapping{english}{english-apa}
\addbibresource{research.bib}
\usepackage{graphicx}
\usepackage{color, colortbl, xcolor}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{longtable}
%\usepackage[outdir=./figs/]{epstopdf}
\usepackage{etoolbox} % for messing with page style & title pages
%\usepackage{fancyhdr}
%\setlength{\headheight}{15.2pt}
%\pagestyle{fancyplain}
%\fancyhf{}
%\lhead{}
%\chead{}
%\rhead{ \fancyplain{}{\thepage} } % put page number in upper right corner
%\rfoot{Compiled on \today\ at \currenttime}
%\renewcommand{\headrulewidth}{0pt} % remove top line
%\renewcommand{\footrulewidth}{0pt} % remove bottom line
%\renewcommand{\headrule}{}%

\title{Expression QTL hotspot dissection with mediation analysis and pleiotropy testing}
\author{Frederick J. Boehm, Brian S. Yandell, and Karl W. Broman}
\date{\today}

@@

<<setup, include=FALSE>>=
library(knitr)
opts_chunk$set(
concordance=TRUE,
echo = TRUE,
fig.lp = "fig:",
warning = FALSE,
message = FALSE)
@

\doublespacing
\listoftodos
\tableofcontents
\listoffigures
\listoftables
%\pagestyle{headings} % page numbers appear at bottom of page, centered!
%\markright{\hfill}
\section{Introduction}

@@

\subsection{Mediation analysis}

For each hotspot and each local trait - nonlocal trait pair, we also performed a
mediation analysis. Each mediation analysis involved fitting four linear models (Equations~\ref{model1}, \ref{model2}, \ref{model3}, \ref{model4}).

\begin{equation}
Y = \alpha 1 + WC + E
\label{model1}
\end{equation}

\begin{equation}
Y = XB + WC + E
\label{model2}
\end{equation}

\begin{equation}
Y = \alpha 1 + WC + M\beta + E
\label{model3}
\end{equation}

\begin{equation}
Y = XB + WC + M\beta + E
\label{model4}
\end{equation}

In all mediation analyses, the nonlocal transcripts are the targets, while the local transcripts serve as candidate mediators of the QTL-target relationship.

@@

<<install_here>>=
install.packages("here", repos = "https://cloud.r-project.org")
@

@@

<<colophon, cache = FALSE>>=
# which R packages and versions?
devtools::session_info()
@

@@

<<git2r, cache = FALSE>>=
# what commit is this file at?
git2r::repository(here::here())
@
